% Created 2017-03-22 Wed 09:19
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\date{Mar 20-24, 2017}
\title{Week 9 lecture notes - PSYC 3435}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.1.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
This week, we'll talk about factorial designs

\section*{Motivation}
\label{sec-1}
So far, all of our experiments have had exactly \textbf{one} independent variable.  What happens when you have two or more?

\subsection*{Example}
\label{sec-1-1}
Suppose you are interested in the effects of modality (visual versus auditory) on memory.  Consider the following experiment:
\begin{itemize}
\item procedure: give participants a list of words to remember
\item IV1: presentation mode (visual, auditory)
\item IV2: test mode (visual, auditory)
\item DV: score on a recognition test ("was this word in the list?")
\end{itemize}

One way to approach this is to run two t-tests on memory scores:
\begin{itemize}
\item Test 1: compare means for visual study and auditory study
\item Test 2: compare means for visual test and auditory test
\end{itemize}

Here's some data (use JASP dataset?):
\begin{itemize}
\item Study mode:
\begin{itemize}
\item visual study: M = 65
\item auditory study: M = 65
\end{itemize}

\item Test mode:
\begin{itemize}
\item visual test: M = 65
\item auditory test: M = 65
\end{itemize}

\item what would we say about the results of our manipulations??
\begin{itemize}
\item no effect of study mode AND no effect of test mode!
\end{itemize}
\end{itemize}

However, we might be missing something:
\begin{itemize}
\item what happens when we consider various combinations of our IVs?
\end{itemize}

Data:

\begin{center}
\begin{tabular}{lrr}
 & visual pres & auditory pres\\
\hline
visual test & 80 & 50\\
auditory test & 50 & 80\\
\end{tabular}
\end{center}

\begin{itemize}
\item what happens when we plot these?
\item what story does this data tell?
\item this is a textbook example of an \emph{interaction}, and is the result of a \textbf{factorial design}
\end{itemize}

\section*{Definitions - Factorial Designs}
\label{sec-2}
\begin{itemize}
\item \emph{factors} - another name for independent variable
\begin{itemize}
\item ex: test mode
\end{itemize}
\item \emph{levels} - the values each factor can take
\begin{itemize}
\item ex: test mode has two levels: visual, auditory
\end{itemize}
\item an N x M factorial design has \emph{two} factors; the first with N levels and the second with M levels
\item Example: in our previous study, we had a 2 x 2 design.
\item Example: consider a 2 x 4 design:
\end{itemize}

\begin{center}
\begin{tabular}{lllll}
 & B1 & B2 & B3 & B4\\
\hline
A1 &  &  &  & \\
A2 &  &  &  & \\
\end{tabular}
\end{center}

The number of \emph{conditions} is calculated by multiplying the numbers of levels, so a 2x4 design has 8 conditions.

\subsection*{Anatomy of a 2x2 design}
\label{sec-2-1}

\begin{center}
\begin{tabular}{llll}
 & A1 & A2 & \\
\hline
B1 & condition mean A1B1 & condition mean A2B1 & marginal mean B1\\
B2 & condition mean A1B2 & condition mean A2B2 & marginal mean B2\\
\hline
 & marginal mean A1 & marginal mean A2 & \\
\end{tabular}
\end{center}

\begin{itemize}
\item if marginal means differ, this is called a \emph{main effect}
\item if pattern in one variable changes across the levels of the other, this is called an \emph{interaction}
\end{itemize}

\subsection*{Advantage of factorial design}
\label{sec-2-2}

If you have only one independent variable, there are only two possible outcomes: there is an effect, or there is not

If you have TWO independent variables, things are much more interesting!

Let 
\begin{itemize}
\item A = main effect of factor A
\item B = main effect of factor B
\item AB = interaction of A and B
\end{itemize}

Then there are EIGHT possible outcomes:
\begin{itemize}
\item No effects at all
\item A only
\item B only
\item AB only
\item A and B, but not AB
\item A and AB, but not B
\item B and AB, but not A
\item A, B, and AB
\end{itemize}

\section*{Examples of 2x2 designs}
\label{sec-3}

For each of the following:
\begin{itemize}
\item compute the marginal means
\item plot the means
\item decide whether the main effects and/or interactions are significant
\end{itemize}

\begin{center}
\begin{tabular}{lrr}
 & A1 & A2\\
\hline
B1 & 30 & 60\\
B2 & 30 & 60\\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{lrr}
 & A1 & A2\\
\hline
B1 & 60 & 60\\
B2 & 30 & 30\\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{lrr}
 & A1 & A2\\
\hline
B1 & 60 & 30\\
B2 & 30 & 60\\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{lrr}
 & A1 & A2\\
\hline
B1 & 30 & 60\\
B2 & 30 & 30\\
\end{tabular}
\end{center}
% Emacs 25.1.1 (Org mode 8.2.10)
\end{document}