% Created 2017-02-02 Thu 14:11
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\date{Jan 30-Feb 3, 2017}
\title{Week 3 lecture notes - PSYC 3435}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.1.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle

\section*{Building a good research question}
\label{sec-1}
\begin{itemize}
\item Suppose we want to claim that people perform best with a good night of sleep
\begin{enumerate}
\item must FOCUS the idea
\begin{itemize}
\item break more general idea into smaller, more specific ideas
\begin{itemize}
\item what do we mean by "performance" -- academic? physical?
\item what do we mean by "good night of sleep" -- 8 hours? uninterrupted? 3 hours of REM?
\end{itemize}
\item develop underlying theoretical model
\begin{itemize}
\item since consolidation of memories happens during REM sleep, we can predict that getting more REM sleep should lead to better recall
\end{itemize}
\end{itemize}
\item must EVALUATE the idea
\begin{itemize}
\item ROT test -- is it:
\begin{itemize}
\item replicable?
\item observable?
\item testable?
\end{itemize}
\end{itemize}
\item TEST the idea
\begin{itemize}
\item what are the variables of interest?
\item what is the hypothesized relationship between these variables?
\item how should we test it?
\end{itemize}
\end{enumerate}
\end{itemize}

\section*{Some definitions}
\label{sec-2}
\begin{itemize}
\item Operational definition - a definition of an abstract concept that is formulated in terms of how the concept is being measured
\begin{itemize}
\item Example: define "memory ability" as score on a memory test
\end{itemize}
\item External validity - the degree to which results of a study apply (generalize) to individuals/behaviors outside context of the study
\item Internal validity - the degree to which a study provides \textbf{causal} information about behavior
\item Reliability - the degree to which the results of a study are consistent under repeated replications
\end{itemize}

\section*{General research methods}
\label{sec-3}
\begin{enumerate}
\item Naturalistic observation: observation and description within a natural setting
\begin{itemize}
\item high external validity
\item hard to do well
\begin{itemize}
\item reactivity effects
\item takes a long time
\item need multiple observers
\end{itemize}
\end{itemize}
\item Survey methods -- questionnaires/interviews that ask people to provide information about themselves
\begin{itemize}
\item widely used
\item best way to collect particular kinds of data (descriptive data, preferences, etc.)
\item large amounts of data very quickly
\item difficult to do correctly with high validity
\end{itemize}
\item Archival data - examine existing public/private records

\item Note: these are all called "observation without manipulation"
\begin{itemize}
\item Advantages:
\begin{enumerate}
\item can observe complex patterns of behavior
\item useful when little is known about subject of study
\item may learn something new that would never have been predicted
\end{enumerate}
\item Disadvantages:
\begin{enumerate}
\item cannot establish causality
\item threats to internal validity
\begin{itemize}
\item lots of "confounds"
\item lots of alternative explanations
\end{itemize}
\item sometimes results are not reproducible
\end{enumerate}
\end{itemize}

\item Correlational methods -- measure two (or more) variables for each individual and see if the variables co-vary (suggesting they are related)
\begin{itemize}
\item used for
\begin{itemize}
\item making predictions
\item establishing reliability and validity
\end{itemize}
\item problem: cannot make causal claims!
\end{itemize}

\item Experiments -- manipulating and controlling variables in laboratory experiments
\begin{itemize}
\item involves some type of comparison
\begin{itemize}
\item at least two groups that get compared (random assignment to groups)
\item quasi-experiment - groups NOT randomly assigned
\end{itemize}
\item types of variables
\begin{itemize}
\item Independent variable (IV) -- variable that is manipulated
\item Dependent variable (DV) -- variable that is measured
\item Control variable -- held constant for all participants in experiment (either through explicit control or randomization)
\end{itemize}
\end{itemize}
\end{enumerate}
\section*{Class activity for Friday}
\label{sec-4}
\begin{enumerate}
\item hand out activity sheet.  Have students return sheets without names
\item talk about False Consensus Effect (Ross et al., 1977; Mullen et al., 1985)
\begin{itemize}
\item Our predictions of others' behaviors tend to err in the direction of our own behaviors
\item Example: Ross et al. (1977) found that college students who preferred brown bread estimated that over 50\% of other college students preferred brown bread, whereas white-bread eaters estimated more accurately that 37\% showed a preference for brown bread.
\item We are going to try to replicate this effect with our data:
\end{itemize}

\item Tasks for students
\begin{itemize}
\item divide into 6 groups\ldots{}assign one question for each group.
\item in each group: tabulate the answers for assigned question and calculate the mean for personal answers.  We'll deal with predicted class mean later.  We will rotate the data sheets through each group in batches until all groups have tabulated all data.
\item Write the question means on the board.
\item Give each student one of the data sheets.
\item Have students compute a score for each data sheet as follows:
\begin{itemize}
\item for each question, score a +1 if personal answer and predicted mean are on same side of mean (that is, both above or both below)
\item score a -1 if personal answer and predicted mean are on opposite sides (that is, one above and one below).
\item sum all 6 questions (+1s and -1s) and get a single integer score between -6 and +6
\item write down that score and return paper to front.
\end{itemize}
\end{itemize}

\item Task for class
\begin{itemize}
\item What would support for False Consensus effect look like?
\item If people err in the direction of their own behavior tendencies, then the mean score should be positive
\item If people err randomly, then the mean score should be 0.
\item do a single-sample t-test on the scores
\end{itemize}
\end{enumerate}
% Emacs 25.1.1 (Org mode 8.2.10)
\end{document}