\documentclass[10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{amsmath}
\usepackage{fancyhdr}
\lhead{PSYC 5316}
\chead{Homework 1}
\cfoot{}
\rhead{Fall 2017}

\pagestyle{fancy}

\begin{document}

\begin{enumerate}
\item For the probability function

\begin{centering}
  \begin{tabular}{cccccc}
    \hline
    $x$ & 1 & 2 & 3 & 4 & 5\\
    $p(x)$ & 0.15 & 0.25 & 0.3 & 0.2 & 0.1\\
    \hline                         
  \end{tabular}\\
\end{centering}

  \begin{enumerate}
    \item compute the mean
    \item compute the variance
    \item plot the distribution in R
  \end{enumerate}

\item For the probability distribution in Exercise 1,
  \begin{enumerate}
  \item what is the probability of observing a value less than or equal to 2?
  \item what is the probability of observing a value greater than 3?
    \item what is the probability of observing a value within one standard deviation of the mean?
    \end{enumerate}


\item For a binomial with $N=15$ and $\theta = 0.6$, what is the probability of observing exactly 2 successes?

\item A coin is rigged so that when it is flipped, the probability of observing ``heads'' is 0.7.  If the coin is flipped three times, which is the more likely outcome: exactly three heads, or two heads and a tail?

\item The Department of Agriculture reports that 75\% of all people who invest in the futures market lose money.  Suppose you are friends with 5 futures traders, each of whom invests independently of the other.  Use a binomial distribution to compute the probability that:
  \begin{enumerate}
  \item all five lose money
  \item all five make money
    \item at least two lose money
  \end{enumerate}


\item Suppose that for a thesis, a colleague has planned 4 independent replications of a basic finding, but has done so quite badly, because their small samples only guarantee power of 30\%.  When your colleague reports the results of their thesis, he reports a statistically significant effect in each of the 4 replications.  A faculty member suggests that it is very likely that your colleague has committed scientific misconduct.  Why?

\item If $X$ is normally distributed with mean $\mu=20$ and standard deviation $\sigma=9$, determine:
  \begin{enumerate}
  \item $P(X<22)$
  \item $P(X>17)$
    \item $P(2<X<38)$
  \end{enumerate}

\item Assuming that the scores on a math achievement test are normally distributed with mean $\mu=68$ and standard deviation $\sigma=10$:

  \begin{enumerate}
  \item what is the probability of getting a score greater than 78?
  \item how high must someone score to be in the top 10\%?
  \end{enumerate}
  
\item Suppose the winnings of gamblers in Las Vegas are normally distributed with mean $\mu=-300$ (the typical person loses \$300), and standard deviation $\sigma = 100$.  Determine the probability that a gambler does NOT lose any money.

\item If $X$ is normally distributed with mean $\mu=100$ and standard deviation $\sigma = 15$, determine $c$ so that
  \[
    P(\mu-c\sigma < X < \mu+c\sigma) = 0.8
  \]

 
\end{enumerate}
\end{document}